---
title: "Australian Weather"
author: "Cory Hyde"
date: "December 20, 2018"
output: ioslides_presentation
---

```{r}




```


## Background on Dataset

- Content is daily observations on Australian Weather
- 1198 Obervations
- 20 Variables 

## Library intro 

```{r}
AUSWeather = read.csv("C:/Users/student/Downloads/AUSWeather.csv")

 library(ggplot2)
 library(lattice)
 library(caret)
 library(glmnet)
 library(ranger)


```

## Humidity 3 PM

```{r}
ggplot(AUSWeather) + geom_point(mapping = aes (x= Humidity3pm , y= Rainfall, color= MaxTemp))





```

## Humidity 9 AM

```{r}
ggplot(AUSWeather) + geom_point(mapping = aes (x= Humidity9am , y= Rainfall, color= MaxTemp))






```

## Pressure 9 AM

```{r}
ggplot(AUSWeather) + geom_point(mapping = aes (x= Pressure9am , y= Rainfall, color= MaxTemp))






```


## Pressure 3 PM

```{r}
ggplot(AUSWeather) + geom_point(mapping = aes (x= Pressure3pm , y= Rainfall, color= MaxTemp))






```

```




## Missing Variables 
 
```{r}
AUSWeather$MinTemp[is.na(AUSWeather$MinTemp)] <- 0
  AUSWeather$MaxTemp[is.na(AUSWeather$MaxTemp)] <- 0
AUSWeather$Rainfall[is.na(AUSWeather$Rainfall)] <- 0
AUSWeather$WindGustSpeed[is.na(AUSWeather$WindGustSpeed)] <- 0
  AUSWeather$WindSpeed9am[is.na(AUSWeather$WindSpeed9am)] <- 0
  AUSWeather$WindSpeed3pm[is.na(AUSWeather$WindSpeed3pm)] <- 0
  AUSWeather$Humidity9am[is.na(AUSWeather$Humidity9am)] <- 0
  AUSWeather$Humidity3pm[is.na(AUSWeather$Humidity3pm)] <- 0
  AUSWeather$Pressure9am[is.na(AUSWeather$Pressure9am)] <- 0
  AUSWeather$Pressure3pm[is.na(AUSWeather$Pressure3pm)] <- 0
  AUSWeather$Cloud9am[is.na(AUSWeather$Cloud9am)] <- 0
  AUSWeather$Cloud3pm[is.na(AUSWeather$Cloud3pm)] <- 0
  AUSWeather$Temp9am[is.na(AUSWeather$Temp9am)] <- 0
  AUSWeather$Temp3pm[is.na(AUSWeather$Temp3pm)] <- 0
  AUSWeather$RISK_MM[is.na(AUSWeather$RISK_MM)] <- 0



```

## Encoding Target Variable 
```{r}
 AUSWeather$RainTomorrow = factor(AUSWeather$RainTomorrow,
levels = c("No","Yes") ,
labels = c(0, 1))



```






## Enconding Wind Directions

```{r}
AUSWeather$WindGustDir = factor(AUSWeather$WindGustDir,
                                 
levels = c("E", "ENE", "ESE", "N", "NE", "NNE", "NNW", "NW", "S", "SE", "SSE", "SSW", "SW", "W", "WNW", "WSW" ) ,
                                 
labels = c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12, 13, 14, 15, 16))







```

## Decision Tree Model 

```{r}

AUSWeather = read.csv("C:/Users/student/Downloads/AUSWeather.csv")

 library(ggplot2)
 library(lattice)
 library(caret)
 library(glmnet)
 library(ranger)


AUSWeather$MinTemp[is.na(AUSWeather$MinTemp)] <- 0
  AUSWeather$MaxTemp[is.na(AUSWeather$MaxTemp)] <- 0
AUSWeather$Rainfall[is.na(AUSWeather$Rainfall)] <- 0
AUSWeather$WindGustSpeed[is.na(AUSWeather$WindGustSpeed)] <- 0
  AUSWeather$WindSpeed9am[is.na(AUSWeather$WindSpeed9am)] <- 0
  AUSWeather$WindSpeed3pm[is.na(AUSWeather$WindSpeed3pm)] <- 0
  AUSWeather$Humidity9am[is.na(AUSWeather$Humidity9am)] <- 0
  AUSWeather$Humidity3pm[is.na(AUSWeather$Humidity3pm)] <- 0
  AUSWeather$Pressure9am[is.na(AUSWeather$Pressure9am)] <- 0
  AUSWeather$Pressure3pm[is.na(AUSWeather$Pressure3pm)] <- 0
  AUSWeather$Cloud9am[is.na(AUSWeather$Cloud9am)] <- 0
  AUSWeather$Cloud3pm[is.na(AUSWeather$Cloud3pm)] <- 0
  AUSWeather$Temp9am[is.na(AUSWeather$Temp9am)] <- 0
  AUSWeather$Temp3pm[is.na(AUSWeather$Temp3pm)] <- 0
  AUSWeather$RISK_MM[is.na(AUSWeather$RISK_MM)] <- 0




```

## Decision Tree  
```{r}
  DecTreeAUS <- train(
    
RainTomorrow~.,
   
data = AUSWeather, method = "rpart",
     
trControl = trainControl(method="cv",number=10,verboseIter = TRUE)) 
  
DecTreeAUS






```

## Conclusion
-Decision Tree was the best model

-Other Models that were used were RandForest and glmnet 

-Decision Tree had accuracy in the high 90's others were mid 80's